Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
rw comment

The main threat to internal validity lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}.
%
\section{Related Work}
\Rui{needs work...}

@@

Prior work has investigated the combination of dynamic slicing and
spectrum-based fault
localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
the methodology used in these papers vary, the overall message is that
the combination is valuable. Note that slicing alone does not provide
the guarantee of improvement to \sfl{} as statements discarded with
slicing could have been ranked lower compared to faulty
statements. This paper differs from prior work in that it uses a much
larger dataset of programs and faults and a more rigorous experimental
methodology.

\section{Conclusions and Future Work}
\label{sec:conc}
%

>>>>

The main threat to internal validity lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}.
%
\section{Related Work}
\Rui{Introductory sentences should say something like: model-based software
debugging, from the DX community, has been shown to be similar to slicing
Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
interesting techniques having been pursued because of scalability. We have
achieved it with a type of program slicing --- critical slicing. Next, we
visit the previous works on program slicing and SFL, without the idea of
being exhaustive, but merely discussing the works that we deem relevant for
this paper.}

\Rui{revisit sentences; check if recent papers are cited.}

@@

Prior work has investigated the combination of dynamic slicing and
spectrum-based fault
localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
the methodology used in these papers vary, the overall message is that
the combination is valuable. Note that slicing alone does not provide
the guarantee of improvement to \sfl{} as statements discarded with
slicing could have been ranked lower compared to faulty
statements. This paper differs from prior work in that it uses a much
larger dataset of programs and faults and a more rigorous experimental
methodology.
%
\section{Conclusions and Future Work}
\label{sec:conc}
%
